Chile Gaps Time

### 2020-01-18 paper.Rmd
site back to root, problem rendenring tables in docs folder
update site in docs

---
title: 'Chile Gaps Time'
author: ""
output:
    html_document:
        smart: false
        toc: true
        number_sections: true
bibliography: "input/bib/My Library.bib"
csl: "input/bib/apa6.csl"
---

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = TRUE)
options(scipen=999)
rm(list=ls())
```

>>>>

---
title: 'Chile Gaps Time'
author: ""
output:
    html_document:
        smart: false
#        toc: true
#        toc_float: true
#        toc_collapsed: true
        number_sections: true
bibliography: "input/bib/My Library.bib"
csl: "input/bib/apa6.csl"
---

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = TRUE)
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
```
